Extension of the approximate static condensation method for multi-material diffusion problems to 3D

### 2019-08-08 3d/asc3d.tex
Update on high order dof

>>>>

{\it Another interpretation of degrees of freedom could be somewhat similar to 2D version.The Lagrange multiplier space in can be defined as}:

$$\Lambda=\left\{\lambda\in \LTwoSpace[{\bfaces[int]}]\,:\, \lambda\in {\widetilde P}_n~\text{for any}~F\in\bfaces[int]\right\}.
$$
\noindent {\it where ${\widetilde P}_n~$ is the polynomial space defined in a
local coordinate system $\{\vect q_1, \vect q_2\}$.
It is convenient to define degrees of freedom for $\lambda\in\Lambda$ in terms
of its~$(n+1)$ moments $\lambda^{(i)}_F$ on every internal face $F\in\bfaces[int]$:

\begin{equation}\label{asc_dofs}
\lambda^{(i)}_F=\frac{\int_F  \lambda\,\phi_i \diff s}{|F|}, \quad i = 0, \dots, n.	\end{equation}
Here~$\{\,\phi_i\,\}_{i=0,\dots,n}$ is the set of {\color{blue}$\LTwoSpace[F]$-orthogonal} polynomials on $F$ of degree~$n$ in a local coordinate system .
}
